\section{RDD Core}
The basic RDD API considers each data item as a single value. However, users often
want to work with key-value pairs. Therefore Spark extended the interface of RDD
to provide additional functions (PairRDDFunctions) which explicitly work on key-value
pairs. Currently, there are four extensions to the RDD API available in spark. They are
as follows:

\bDoubleRDDFunctions This extension contains many useful methods for aggregating
numeric values. They become available if the data items of an RDD are implicitly
convertible to the Scala data-type \textbf{double}.

\bPairRDDFunctions Methods defined in this interface extension become available when
the data items have a two component \textbf{tuple structure [K,V]}. Spark will interpret the first
tuple item (i.e. tuplename. 1) as the key and the second item (i.e. tuplename. 2)
as the associated value.

\bOrderedRDDFunctions Methods defined in this interface extension become available if
the data items are two component tuples where the key is implicitly \textbf{sortable}.

\bSequenceFileRDDFunctions This extension contains several methods that allow users
to create \textbf{Hadoop sequence-files from RDDs}. The data items must be two compo-
nent key-value tuples as required by the PairRDDFunctions. However, there are
additional requirements considering the convertibility of the tuple components to
Writable types.

Since Spark will make methods with extended functionality automatically available
to users when the data items fulfill the above described requirements, we decided to list
all possible available functions in strictly alphabetical order. We will append either of
the following flags [Double] , [Ordered], [Pair] or [SeqFile] to the function-name to indicate it
belongs to an extension that requires the data items to conform to a certain format or
type.

Learn by example usage:
Care is taken to make sure individual example can be directly tested on Spark shell...Enjoy!
\bRefer: org.aja.tej.test.spark.rdd for example and explanations!
Ctrl + B on the method to see its definition!